---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# n3<span style="color:#84aff5">R</span>gy

A lightweight R package for interfacing with the [n3rgy](https://data.n3rgy.com/consumer/home) consumer API to access UK smart meter electricity data.

Before using this package you will need to have followed the instructions at the link above, providing n3rgy with the MPxN and MAC numbers for your smart meter.

## Installation

``` r
install.packages("remotes")
remotes::install_github("odaniel1/n3Rgy")
```

## Example

Get information about your electricity tariff:
```r
library(n3Rgy)
# Examples WILL NOT RUN without a valid MAC number
my_mac <- "<insert your MAC here>"

tariff <- n3rgy_tariff(my_mac, from = "2023-08-01", to = "2023-08-01")

tariff$standing_charge
```
```{r echo = FALSE}
library(n3Rgy)
tariff_example$standing_charge
```
```r
head(tariff_example$price_per_kWh)
```
```{r echo = FALSE}
head(tariff_example$price_per_kWh)
```

Or get your electricity consumption over time:

```r
consumption <- n3rgy_consumption(my_mac, from = "2023-08-01", to = "2023-08-01")

library(ggplot2)

ggplot(consumption) +
  geom_col(aes(timestamp, consumption_kWh)) +
  theme_minimal()
```
```{r echo = FALSE,fig.width=8,fig.height=5}
library(n3Rgy)
library(ggplot2)
ggplot(consumption_example) +
  geom_col(aes(timestamp, consumption_kWh)) +
  theme_minimal()
```
