---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# n3<span style="color:#84aff5">R</span>gy

[n3rgy](https://data.n3rgy.com/consumer/home) provide UK energy consumers with free access to their smart meter data, enabling people to track their energy use over time.

This R package, n3**R**gy, provides a lightweight interface with the consumer API. This is not an official product of n3rgy.

## Get Started
 
Before using this package you will need to have followed the steps on n3rgy's [website](https://data.n3rgy.com/consumer/home), providing the MPxN and MAC numbers for smart meter you want data from. These numbers should both be accessible from your smart meter's In-Home Display (IHD).

Retain a copy of your MAC number to hand as this will be needed when interfacing with the API.

With that done, its time to install the n3Rgy package:

``` r
install.packages("remotes")
remotes::install_github("odaniel1/n3Rgy")
```

## Usage
The package has two functions: `n3rgy_tariff` and `n3rgy_consumption`. To use both
you will need to provide your MAC number.

`n3rgy_tariff` returns information about your current and previous energy
tariffs, including your daily standing charge and price per kilowatt hour at half-hour
intervals. 

```r
library(n3Rgy)
# Examples WILL NOT RUN without a valid MAC number
my_mac <- "<insert your MAC here>"

tariff <- n3rgy_tariff(my_mac, from = "2023-08-01", to = "2023-08-01")

tariff$standing_charge
```
```{r echo = FALSE}
library(n3Rgy)
tariff_example$standing_charge
```
```r
head(tariff_example$price_per_kWh)
```
```{r echo = FALSE}
head(tariff_example$price_per_kWh)
```

Whilst `n3rgy_consumption` returns the electricity consumed, aggregated to half-hour intervals.

```r
consumption <- n3rgy_consumption(my_mac, from = "2023-08-01", to = "2023-08-01")

library(ggplot2)

ggplot(consumption) +
  geom_col(aes(timestamp, consumption_kWh)) +
  theme_minimal()
```
```{r echo = FALSE,fig.width=8,fig.height=5}
library(n3Rgy)
library(ggplot2)
ggplot(consumption_example) +
  geom_col(aes(timestamp, consumption_kWh)) +
  theme_minimal()
```
